STA302 Final Project Proposal

### 2024-10-11 paper/proposal.qmd
Update proposal.qmd

boxplot(y_value ~ data$owners , main="Residual vs Owners",
xlab="Owners", ylab="Residuals")
```
## Create Normal QQ Plot to check Normality assumption
```{r}
#| echo: false
#| warning: false
#| message: false
qqnorm(y_value)
qqline(y_value)
```

\newpage

>>>>

boxplot(y_value ~ data$owners , main="Residual vs Owners",
xlab="Owners", ylab="Residuals")
```
## Create Normal QQ Plot to check Normality assumption
```{r}
#| echo: false
#| warning: false
#| message: false
qqnorm(y_value)
qqline(y_value)
```
The four linear regression assumptions to be looked into are linearity, uncorrelated errors, constant error variance, and normality. Since this is a multiple linear regression, we must also check the conditional mean response and predictor conditions. To check the conditional mean response condition, we look at the Response vs. Fitted scatterplot. We see an that the data points are clustered fairly tightly in the bottom left corner of the scatterplot, which satisfies the condition. To check the conditional mean predictors assumption, we must look at the pairwise scatterplots of predictors, in which we see a lack of curves which satisfies this condition as well. When looing at the Residual vs. Fitted scatterplot, we can see a fanning pattern in the shape of a left pointing arrow, which leads to a possible violation of the constant variance assumption. Looking at the Residuals vs. Qualitative Predictor scatterplots suggests a possible violation of both linearity and uncorrelated errors due to the cluster of many points in all three as well as the curves that exist in the positive and negative ratings. Neither of the boxplots appear to suggest any kind of linear assumption violation regarding the categorical predictors. Looking at the Normal QQ Plot, there is some deviation from the diagonal at the extremes that appears to be too significant to ignore. This leads to a normality violation. 
\newpage
